2H qSIP Calculations

### 2021-10-27 qSIP_calculations.Rmd
LOTS O' PLOTS

```{r, message=FALSE, warning=FALSE}
library(tidyverse) # general data wrangling and plotting
library(isoreader) # reading the raw data files
library(isoprocessor) # processing the data
library(isotopia) # isotope utilities
library(readxl) # reading excel docs
library(ggsci) # some nice color palettes
library(ggborderline) # nice looking ggplot lines
library(ggrepel)
library(latex2exp)
library(ggdist)
library(ggsignif)

source(file.path("libs", "visualization.R"))
source(file.path("libs", "chromleon.R"))
`%nin%` = Negate(`%in%`)
```

@@

## Load Metadata and Problematic Run Data

@@

## Load Peak Map

@@

### Unnest integration details

## Read raw IRMS data files

```{r, warning=FALSE}
# set file path(s) to data files, folders or rds collections 
# can be multiple folders or mix of folders and files
# setting the month of analysis folder - Isoverse will iteratively search subfolders. Huzzah! ^_^
data_path <- file.path("data", "IRMS", "2021-09")
ref_ratio <- get_standard("2H") %>% as.numeric()

@@

## Process file info & peak table

@@

## Show file information

@@

## Example chromatograms

@@

@@

## Extract zero timepoint values
```{r}
zero_peaks <- peaks_mapped %>%
  filter(inc_time_d_str == "0 Days") %>%
  group_by(t_series_id, compound) %>%
  mutate(n_analyical_reps = n()) %>%
  ungroup() %>%
  # exclude ambiguous peaks and those with multiple data points
  # this needs to be fixed
  filter(!is_ambiguous, n_analyical_reps == 1)

@@

```{r}
# Combine triplicate samples into one
FID_results_trip <- FID_results %>% 
  # Remove standards and fractions
  filter(sample != "FAME37.1") %>% 
  filter(sample != "TCBAME-2") %>% 
  filter(!str_detect(sample, "F1")) %>% 
  filter(!str_detect(sample, "F2")) %>% 
  filter(!str_detect(sample, "F3")) %>% 
  filter(!str_detect(sample, "cr")) %>%
  mutate(sample_rep = str_remove(sample, "[xyz]")) %>% 
  group_by(sample_rep, `Peak Name`) %>%
  # Generate summary stats
  summarize(rel_area_max = max(`Relative Area`, na.rm=TRUE),
            rel_area_min = min(`Relative Area`, na.rm=TRUE),
            rel_height_max = max(`Relative Height`, na.rm=TRUE),
            rel_height_min = min(`Relative Height`, na.rm=TRUE),
            `Retention Time` = mean(`Retention Time`, na.rm=TRUE),
            `Relative Area` = mean(`Relative Area`, na.rm=TRUE),
            `Relative Height` = mean(`Relative Height`, na.rm=TRUE)) %>% 
  # Add some basic metadata
  mutate(inc_time = case_when(
    str_detect(sample_rep, "...0") ~ 0,
    str_detect(sample_rep, "...3") ~ 3,
    str_detect(sample_rep, "...7") ~ 7),
    site = case_when(
      str_detect(sample_rep, "c") ~ "Conifer",
      str_detect(sample_rep, "t") ~ "Tundra",
      str_detect(sample_rep, "g") ~ "Grassland",
      str_detect(sample_rep, "m") ~ "Meadow")
  )
```

## Remove standards from gencalcs
```{r}
# Don't want our standard compounds to be used for generation time calculations! x_x
peaks_mapped_with_zeros_analytes <- peaks_mapped_with_zeros %>% 
  filter(str_detect(compound, "STD", negate = TRUE))
```

@@

```{r}
gen_calc_data <- peaks_mapped_with_zeros_analytes %>% 
  mutate(
    f_label = 0.5, # label is 0.5 at%
    a = 0.5, # assimilation efficiency
    t0 = 0, # start time
    f_start = at2H_mn_zero,
    d_t = inc_time_d - t0, # change in time
    f_t = at2H, # restate 2F at time t
    u_d = gencalc(a = 0.5, # Assimilation efficiency
                  FT = f_t, # 2F at time t (at%)
                  F0 = f_start, # 2F at t0 (at%)
                  FL = f_label, # 2F of label (at%)
                  t = d_t), # change in time
         # Returns turnover (µ) in days^-1
         gen_d = log(2) / u_d # calculate generation time
  )

@@

```{r}
peaks_mapped_with_zeros_analytes %>% ggplot(
  aes(x = inc_time_d, y = at2H, color = compound, group = compound)) +
  geom_point() +
  #geom_borderline() +
  scale_color_viridis_d() +
  theme_minimal()
```

@@

@@

```{r}
p_gen_time_dist <- gen_calc_data %>% filter(inc_time_d != 0) %>% 
  ggplot(
  aes(x = gen_d, 
      y = inc_time_d_str, 
      color = inc_time_d_str, 
      fill = inc_time_d_str)) +
  stat_slab(height = 0.3, alpha = 0.7) +
  # stat_pointinterval(color = "black") +
  geom_boxplot(fill = "white",
               color = "black",
               width = 0.1,
               outlier.shape = NA) +
  geom_point(
    color = "black",
    #shape = 124,
    #size = 3,
    alpha = 0.5,
    position = position_nudge(y = -.03)) +
  # geom_text_repel(aes(label = compound), 
  #                 color = "black", 
  #                 nudge_y = -0.3, 
  #                 size = 3) +
  scale_x_log10() +
  annotation_logticks(sides = "b") +
  scale_fill_npg() +
  scale_color_npg() +
  theme_classic() +
  labs(x = "Generation time (days)",
       y = "Incubation time",
       title = "Generation times of soil bacteria",
       subtitle = "Lipid-specific generation times of bacteria",
       caption = "Soils collected from Colorado") +
  theme(legend.position = "none",
        axis.ticks.y = element_blank())
p_gen_time_dist

@@

```{r}
p_gen_time_dist_all <- gen_calc_data %>% filter(inc_time_d != 0) %>% 
  ggplot(
  aes(x = gen_d, 
      y = 1)) +
  stat_halfeye(height = 0.1, 
            alpha = 0.7,
            color = "black") +
  geom_jitter(aes(y = 0.9, 
                 color = inc_time_d_str),
             alpha = 0.5,
             height = 0.03,
             size = 1) +
  # geom_text_repel(aes(label = compound), 
  #                 color = "black", 
  #                 nudge_y = -0.3, 
  #                 size = 3) +
  scale_x_log10() +
  coord_cartesian(ylim = c(0.5, 1.25)) +
  annotation_logticks(sides = "b") +
  scale_fill_npg() +
  scale_color_npg() +
  theme_classic() +
  labs(x = "Generation time (days)",
       title = "Generation times of soil bacteria",
       subtitle = "Lipid-specific generation times of bacteria",
       caption = "Soils collected from Colorado",
       color = "Incubation Time") +
  theme(legend.position = "bottom",
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y = element_blank())
p_gen_time_dist_all
```

@@

```{r}
p_gen_time_dist_all_lin <- gen_calc_data %>% 
  filter(inc_time_d != 0,
         gen_d >= 0) %>% 
  ggplot(
  aes(x = u_d, 
      y = 1)) +
  stat_halfeye(height = 0.25, 
            alpha = 0.7,
            color = "black") +
  geom_jitter(aes(y = 0.9, 
                 color = inc_time_d_str),
             alpha = 0.5,
             height = 0.03,
             size = 1) +
  # geom_text_repel(aes(label = compound), 
  #                 color = "black", 
  #                 nudge_y = -0.3, 
  #                 size = 3) +
  coord_cartesian(ylim = c(0.8, 1.25)) +
  scale_fill_npg() +
  scale_color_npg() +
  theme_classic() +
  labs(x = "Turnover Time (d^-1)",
       title = "Turnover Times",
       subtitle = "Lipid-specific turnover times of bacteria",
       caption = "Soils collected from Colorado",
       color = "Incubation Time") +
  theme(legend.position = "bottom",
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y = element_blank())
p_gen_time_dist_all_lin
```

@@

```{r}
p_gen_time_terrain <- gen_calc_data %>% filter(inc_time_d != 0) %>% 
  ggplot(
  aes(x = gen_d, 
      y = terrain, 
      color = terrain, 
      fill = terrain)) +
  stat_slab(height = 0.3, alpha = 0.7) +
  stat_pointinterval(color = "black") +
  geom_point(
    color = "black",
    shape = 124,
    size = 3,
    alpha = 0.5,
    position = position_nudge(y = -.03)) +
  # geom_text_repel(aes(label = compound), 
  #                 color = "black", 
  #                 nudge_y = -0.3, 
  #                 size = 3) +
  scale_x_log10() +
  annotation_logticks(sides = "b") +
  scale_fill_npg() +
  scale_color_npg() +
  theme_classic() +
  labs(x = "Generation time (days)",
       y = "Terrain",
       title = "Generation times of soil bacteria across terrain")
  theme(legend.position = "none",
        axis.ticks.y = element_blank())
p_gen_time_terrain
```

@@

```{r}
gen_calc_data %>% filter(inc_time_d != 0) %>% 
  ggplot(aes(x = compound, y = u_d, color = terrain)) +
  facet_wrap(vars(terrain, inc_time_d_str)) +
  geom_point() +
  theme_bw() +
  labs(x = "Compound",
       y = "Turnover time (d^-1)",
       title = "Compound-specific turnover rates of bacterial phospholipid fatty acids") +
  theme(
    axis.text.x = element_text(angle = 90)
  )
```

## Generation Time, Broken by Terrain and Incubation Time

```{r}
p_gen_time_terrain_inc <- gen_calc_data %>% filter(inc_time_d != 0) %>% 
  ggplot(
  aes(x = gen_d, 
      y = inc_time_d_str, 
      color = soil_id, 
      fill = soil_id)) +
  stat_slab(height = 0.3, alpha = 0.7) +
  stat_pointinterval(color = "black") +
  geom_point(
    color = "black",
    shape = 124,
    size = 3,
    alpha = 0.5,
    position = position_nudge(y = -.03)) +
  # geom_text_repel(aes(label = compound), 
  #                 color = "black", 
  #                 nudge_y = -0.3, 
  #                 size = 3) +
  facet_wrap(~soil_id, ncol = 1) +
  scale_x_log10() +
  annotation_logticks(sides = "b") +
  scale_fill_npg() +
  scale_color_npg() +
  theme_classic() +
  labs(x = "Generation time (days)",
       y = "Terrain",
       title = "Generation times of soil bacteria across terrain")
  theme(legend.position = "none",
        axis.ticks.y = element_blank())
p_gen_time_terrain_inc
```

@@

```{r}
p_turnover_terrain <- gen_calc_data %>% filter(inc_time_d != 0) %>% 
  ggplot(
  aes(x = inc_time_d_str, 
      y = u_d, 
      color = terrain, 
      fill = terrain)) +
  #stat_slab(height = 0.3, alpha = 0.7) +
  stat_pointinterval(color = "black") +
  geom_point(
    color = "black",
    #shape = 124,
    size = 1,
    alpha = 0.5,
    position = position_nudge(x = -.03)) +
  # geom_text_repel(aes(label = compound), 
  #                 color = "black", 
  #                 nudge_y = -0.3, 
  #                 size = 3) +
  facet_wrap(~terrain, nrow = 1) +
  scale_y_log10() +
  annotation_logticks(sides = "a") +
  scale_fill_npg() +
  scale_color_npg() +
  theme_bw() +
  labs(x = "Generation time (days)",
       y = "Terrain",
       title = "Generation times of soil bacteria across terrain")
  theme(legend.position = "none",
        axis.ticks.y = element_blank())
p_turnover_terrain
```

@@

```{r}
p_turnover_terrain_7d <- gen_calc_data %>% filter(inc_time_d == 7) %>% 
  ggplot(
  aes(x = terrain, 
      y = u_d)) +
  #stat_slab(height = 0.3, alpha = 0.7) +
  #stat_pointinterval(color = "black") +
  geom_boxplot(outlier.shape = NA) +
  geom_point(
    color = "black",
    #shape = 124,
    size = 1,
    alpha = 0.5) +
  # geom_text_repel(aes(label = compound), 
  #                 color = "black", 
  #                 nudge_y = -0.3, 
  #                 size = 3) +
  scale_y_log10() +
  annotation_logticks(sides = "a") +
  scale_fill_npg() +
  scale_color_npg() +
  theme_bw() +
  labs(x = "Terrain",
       y = "Turnover time (d^-1)",
       title = "Generation times of soil bacteria across terrain") +
  theme(legend.position = "none",
        axis.ticks.y = element_blank())
p_turnover_terrain_7d
```

@@

@@

```{r}
# coming soon!
```

## Compound Abundance Versus Turnover Time
```{r}
# coming soon!
```

>>>>

```{r, message=FALSE, warning=FALSE}
# Libraries
library(tidyverse) # general data wrangling and plotting
library(forcats) # handling factors
library(isoreader) # reading the raw data files
library(isoprocessor) # processing the data
library(isotopia) # isotope utilities
library(readxl) # reading excel docs
library(ggsci) # some nice color palettes
library(ggborderline) # nice looking ggplot lines
library(ggrepel) # nice looking ggplot labels
library(latex2exp) # latex parsing
library(ggdist) # ggplot distribution geoms
library(ggsignif) # ggplot significance markers
library(ggridges) # ggplot ridgeline geoms

# Sourced Functions
source(file.path("libs", "visualization.R"))
source(file.path("libs", "chromleon.R"))
`%nin%` = Negate(`%in%`)
```

@@

## Load IRMS Data

### Load Metadata and Problematic Run Data

@@

### Load Peak Map

@@

### Read raw IRMS data files

```{r, warning=FALSE}
# Set file path(s) to data files, folders or rds collections 
# can be multiple folders or mix of folders and files
# Isoverse will iteratively search subfolders. Huzzah! ^_^
data_path <- file.path("data", "IRMS", "raw_data")
ref_ratio <- get_standard("2H") %>% as.numeric()

@@

### Process file info & peak table

@@

### Show file information

@@

### Example chromatograms

@@

### Unnest FID integration details

@@

## Extract zero timepoint values
```{r}
zero_peaks <- peaks_mapped %>%
  filter(inc_time_d_str == "0 Days") %>%
  group_by(t_series_id, compound) %>%
  mutate(n_analyical_reps = n()) %>%
  ungroup() %>%
  # exclude ambiguous peaks
  filter(!is_ambiguous)

@@

```{r}
# Combine triplicate samples into one
FID_results_trip <- FID_results %>% 
  # Remove standards and fractions
  filter(sample_id != "FAME37.1") %>% 
  filter(sample_id != "TCBAME-2") %>% 
  filter(!str_detect(sample_id, "F1")) %>% 
  filter(!str_detect(sample_id, "F2")) %>% 
  filter(!str_detect(sample_id, "F3")) %>% 
  filter(!str_detect(sample_id, "cr")) %>%
  mutate(sample_rep = str_remove(sample_id, "[xyz]")) %>% 
  group_by(sample_rep, compound) %>%
  # Generate summary stats
  summarize(rel_area_FID_max = max(rel_area_FID, na.rm=TRUE),
            rel_area_FID_min = min(rel_area_FID, na.rm=TRUE),
            rel_height_FID_max = max(rel_height_FID, na.rm=TRUE),
            rel_height_FID_min = min(rel_height_FID, na.rm=TRUE),
            rt_FID = mean(rt_FID, na.rm=TRUE),
            rel_area_FID = mean(rel_area_FID, na.rm=TRUE),
            rel_height_FID = mean(rel_height_FID, na.rm=TRUE)) %>% 
  # Add some basic metadata
  mutate(inc_time = case_when(
    str_detect(sample_rep, "...0") ~ 0,
    str_detect(sample_rep, "...3") ~ 3,
    str_detect(sample_rep, "...7") ~ 7),
    site = case_when(
      str_detect(sample_rep, "c") ~ "Conifer",
      str_detect(sample_rep, "t") ~ "Tundra",
      str_detect(sample_rep, "g") ~ "Grassland",
      str_detect(sample_rep, "m") ~ "Meadow")
  )
```

## Remove standards from gencalcs
```{r}
# Don't want our standard compounds to be used for generation time calculations! x_x
peaks_mapped_with_zeros_analytes <- peaks_mapped_with_zeros_FID %>% 
  filter(str_detect(compound, "STD", negate = TRUE))
```

## Summarize Analytical and Experimental Replicates

```{r}
peaks_mapped_summarized <- peaks_mapped_with_zeros_analytes %>% 
  group_by(terrain, inc_time_d, compound) %>% 
  summarize_if(is.numeric, mean, na.rm = TRUE)
```

## Calculate turnover time
Turnover is calculated as below:

$$
\mu = - \frac{1}{t} \cdot (ln (\frac{F_T - a \cdot F_L}{F_0 - a \cdot F_L})
$$

```
# R code:
gencalc <- function(a, FT, F0, FL, t) {
  case_when(
    t == 0 ~ NA_real_,
    TRUE ~ - (1/t)*(log((FT - a*FL)/(F0 - a*FL)))
  )
}

@@

```{r}
gen_calc_data <- peaks_mapped_with_zeros_analytes %>% 
  mutate(
    f_label = 0.5, # label is 0.5 at%
    a = 0.5, # assimilation efficiency
    t0 = 0, # start time
    f_start = at2H_mn_zero,
    d_t = inc_time_d - t0, # change in time
    f_t = at2H, # restate 2F at time t
    u_d = gencalc(a = 0.5, # Assimilation efficiency
                  FT = f_t, # 2F at time t (at%)
                  F0 = f_start, # 2F at t0 (at%)
                  FL = f_label, # 2F of label (at%)
                  t = d_t), # change in time
    # "negative" turnovers are artifacts of noise and should be zero
    u_d = if_else(u_d < 0, 0, u_d),
    # calculate generation time, converting negatives to zero
    gen_d = if_else(u_d < 0, 0, log(2) / u_d)
  ) %>%
  mutate(
    chain_fctr = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs() %>% 
      {paste0("C", .)} %>% 
      factor()
      ) %>% 
  mutate(
    chain_num = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs()
  )

gen_calc_data_summarized <- peaks_mapped_summarized %>% 
  mutate(
    f_label = 0.5, # label is 0.5 at%
    a = 0.5, # assimilation efficiency
    t0 = 0, # start time
    f_start = at2H_mn_zero,
    d_t = inc_time_d - t0, # change in time
    f_t = at2H, # restate 2F at time t
    u_d = gencalc(a = 0.5, # Assimilation efficiency
                  FT = f_t, # 2F at time t (at%)
                  F0 = f_start, # 2F at t0 (at%)
                  FL = f_label, # 2F of label (at%)
                  t = d_t), # change in time
    # "negative" turnovers are artifacts of noise and should be zero
    u_d = if_else(u_d < 0, 0, u_d),
    # calculate generation time, converting negatives to zero
    gen_d = if_else(u_d < 0, 0, log(2) / u_d)
  ) %>%
  mutate(
    chain_fctr = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs() %>% 
      {paste0("C", .)} %>% 
      factor()
      ) %>% 
  mutate(
    chain_num = compound %>% 
      str_remove("\\d+-OH") %>% 
      parse_number() %>% 
      abs()
  )

@@

## Peak Tracer Incorporation
```{r}
peaks_mapped_with_zeros_analytes %>% ggplot(
  aes(x = inc_time_d, y = at2H, color = compound, group = compound)) +
  geom_point() +
  geom_smooth(se = FALSE,
              method = "loess") +
  #geom_borderline() +
  scale_color_viridis_d() +
  theme_minimal()
```

@@

## Compound enrichment over time

```{r}
gen_calc_data_summarized %>% 
  mutate(compound = fct_reorder(compound, rt)) %>% 
  ggplot(aes(x = inc_time_d,
             y = at2H,
             color = compound)) +
  geom_borderline() +
  geom_point() +
  facet_wrap(vars(terrain)) +
  scale_x_continuous(breaks = c(0, 3, 7)) +
  scale_color_viridis_d() +
  theme_bw() +
  labs(x = "Incubation Time (Days)",
       y = "Mean %D")
```

## Compound enrichment over time with label strength

```{r}
gen_calc_data_summarized %>% 
  filter(compound != "i-16:0") %>% 
  mutate(compound = fct_reorder(compound, rt)) %>% 
  ggplot(aes(x = inc_time_d,
             y = at2H,
             color = compound)) +
  geom_point() +
  geom_borderline() +
  geom_hline(yintercept = 0.5,
             color = "red") +
  facet_wrap(vars(terrain)) +
  scale_x_continuous(breaks = c(0, 3, 7)) +
  scale_color_viridis_d() +
  labs(x = "Incubation Time (Days)",
       y = "Mean %D") +
  theme_bw()
```

@@

```{r}
p_gen_time_dist <- gen_calc_data %>% 
  filter(inc_time_d != 0) %>% 
  ggplot(
  aes(y = gen_d, 
      x = inc_time_d_str, 
      color = inc_time_d_str, 
      fill = inc_time_d_str)) +
  stat_slab(width = 0.3, alpha = 0.7) +
  stat_pointinterval(color = "black") +
  # geom_boxplot(fill = "white",
  #              color = "black",
  #              width = 0.1,
  #              outlier.shape = NA) +
  geom_point(
    color = "black",
    shape = 95,
    size = 3,
    alpha = 0.5,
    position = position_nudge(x = -.03)) +
  # geom_text_repel(aes(label = compound), 
  #                 color = "black", 
  #                 nudge_y = -0.3, 
  #                 size = 3) +
  scale_y_log10() +
  annotation_logticks(sides = "l") +
  scale_fill_npg() +
  scale_color_npg() +
  theme_classic() +
  labs(y = "Generation time (days)",
       x = "Incubation time",
       title = "Generation times of soil bacteria",
       subtitle = "Lipid-specific generation times of bacteria",
       caption = "Soils collected from Colorado") +
  theme(legend.position = "none",
        axis.ticks.y = element_blank())
p_gen_time_dist

@@

```{r}
p_gen_time_dist_all <- gen_calc_data %>% filter(inc_time_d != 0) %>% 
  ggplot(
  aes(y = gen_d, 
      x = 1)) +
  stat_slab(width = 0.3, alpha = 0.7) +
  stat_pointinterval(color = "black") +
  # geom_boxplot(fill = "white",
  #              color = "black",
  #              width = 0.1,
  #              outlier.shape = NA) +
  geom_point(
    color = "black",
    shape = 95,
    size = 3,
    alpha = 0.5,
    position = position_nudge(x = -.03)) +
  # geom_text_repel(aes(label = compound), 
  #                 color = "black", 
  #                 nudge_y = -0.3, 
  #                 size = 3) +
  scale_y_log10() +
  annotation_logticks(sides = "l") +
  scale_fill_npg() +
  scale_color_npg() +
  theme_classic() +
  labs(y = "Generation time (days)",
       title = "Generation times of soil bacteria",
       subtitle = "Lipid-specific generation times of bacteria",
       caption = "Soils collected from Colorado") +
  theme(legend.position = "none",
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        axis.title.x = element_blank())
p_gen_time_dist_all
```

## Generation Time, all points, not separated, > C19 removed

```{r}
p_gen_time_dist_all_no19 <- gen_calc_data %>% 
  filter(inc_time_d != 0,
         chain_num < 19) %>% 
  ggplot(
  aes(y = gen_d, 
      x = 1)) +
  stat_slab(width = 0.3, alpha = 0.7) +
  stat_pointinterval(color = "black") +
  # geom_boxplot(fill = "white",
  #              color = "black",
  #              width = 0.1,
  #              outlier.shape = NA) +
  geom_point(
    color = "black",
    shape = 95,
    size = 3,
    alpha = 0.5,
    position = position_nudge(x = -.03)) +
  # geom_text_repel(aes(label = compound), 
  #                 color = "black", 
  #                 nudge_y = -0.3, 
  #                 size = 3) +
  scale_y_log10() +
  annotation_logticks(sides = "l") +
  scale_fill_npg() +
  scale_color_npg() +
  theme_classic() +
  labs(y = "Generation time (days)",
       title = "Generation times of soil bacteria",
       subtitle = "Lipid-specific generation times of bacteria \nC20+ removed",
       caption = "Soils collected from Colorado") +
  theme(legend.position = "none",
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        axis.title.x = element_blank())
p_gen_time_dist_all_no19
```

@@

```{r}
p_gen_time_dist_all_lin <- gen_calc_data %>% 
  filter(inc_time_d != 0,
         gen_d >= 0,
         chain_num < 19) %>% 
  ggplot(
  aes(y = gen_d, 
      x = 1)) +
  stat_slab(width = 0.25, 
            alpha = 0.7,
            color = "black") +
  stat_pointinterval(color = "black") +
  # geom_boxplot(fill = "white",
  #              color = "black",
  #              width = 0.1,
  #              outlier.shape = NA) +
  geom_point(
    color = "black",
    shape = 95,
    size = 3,
    alpha = 0.5,
    position = position_nudge(x = -.03)) +
  # geom_text_repel(aes(label = compound), 
  #                 color = "black", 
  #                 nudge_y = -0.3, 
  #                 size = 3) +
  scale_fill_npg() +
  scale_color_npg() +
  theme_classic() +
  labs(y = "Generation time (days)",
       title = "Generation times of soil bacteria",
       subtitle = "Lipid-specific generation times of bacteria",
       caption = "Soils collected from Colorado") +
  theme(legend.position = "none",
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        axis.title.x = element_blank())
p_gen_time_dist_all_lin
```

@@

```{r}
signif_comparisons <- gen_calc_data %>% pull(terrain) %>% unique()

p_gen_time_terrain <- gen_calc_data %>% 
  filter(inc_time_d != 0,
         chain_num < 19) %>% 
  ggplot(
  aes(y = gen_d, 
      x = terrain,
      color = terrain,
      fill = terrain)) +
  stat_slab(width = 0.25, 
            alpha = 0.7,
            color = "black") +
  stat_pointinterval(color = "black") +
  # geom_boxplot(fill = "white",
  #              color = "black",
  #              width = 0.1,
  #              outlier.shape = NA) +
  geom_point(
    color = "black",
    shape = 95,
    size = 3,
    alpha = 0.5,
    position = position_nudge(x = -.07)) +
  geom_signif(comparisons = list(signif_comparisons),
              map_signif_level = TRUE) +
  scale_y_log10(breaks = c(1, 10, 100)) +
  annotation_logticks(sides = "l") +
  scale_fill_npg() +
  scale_color_npg() +
  theme_classic() +
  labs(y = "Generation time (days)",
       title = "Generation times of soil bacteria",
       subtitle = "Lipid-specific generation times of bacteria \nC20+ omitted") +
  theme(axis.ticks.y = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1))
p_gen_time_terrain
```

@@

```{r}
gen_calc_data %>% filter(inc_time_d != 0) %>% 
  mutate(compound = fct_reorder(compound, rt)) %>% 
  ggplot(aes(x = compound,
             y = u_d, 
             color = terrain, 
             fill = terrain)) +
  facet_wrap(vars(terrain, inc_time_d_str),
             ncol = 2) +
  geom_segment(aes(xend = compound,
                   yend = 0),
               color = "black") +
  geom_point() +
  scale_color_npg() +
  labs(x = "Compound",
       y = "Turnover time (d^-1)",
       title = "Compound-specific turnover rates of bacterial phospholipid fatty acids",
       color = "Terrain",
       fill = "Terrain") +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 90, 
                               hjust = 1)
  )
```

@@

```{r}
p_turnover_terrain <- gen_calc_data %>% filter(inc_time_d != 0) %>% 
  ggplot(
  aes(x = inc_time_d_str, 
      y = u_d, 
      color = terrain, 
      fill = terrain)) +
  #stat_slab(height = 0.3, alpha = 0.7) +
  stat_pointinterval(color = "black") +
  # geom_point(
  #   color = "black",
  #   #shape = 124,
  #   size = 1,
  #   alpha = 0.5,
  #   position = position_nudge(x = -.05)) +
  # geom_text_repel(aes(label = compound), 
  #                 color = "black", 
  #                 nudge_y = -0.3, 
  #                 size = 3) +
  facet_wrap(~terrain, nrow = 1) +
  scale_y_log10() +
  annotation_logticks(sides = "a") +
  scale_fill_npg() +
  scale_color_npg() +
  theme_bw() +
  labs(x = "Incubation Time",
       y = "Turnover Time (d^-1)",
       title = "Generation times of soil bacteria across terrain")
  theme(legend.position = "none",
        axis.ticks.y = element_blank())
p_turnover_terrain
```

@@

```{r}
p_turnover_terrain_7d <- gen_calc_data %>% filter(inc_time_d == 7) %>% 
  ggplot(
  aes(x = terrain, 
      y = u_d)) +
  #stat_slab(height = 0.3, alpha = 0.7) +
  #stat_pointinterval(color = "black") +
  geom_boxplot(outlier.shape = NA) +
  geom_point(
    color = "black",
    #shape = 124,
    size = 1,
    alpha = 0.5) +
  geom_signif(comparisons = list(signif_comparisons),
              map_signif_level = TRUE) +
  scale_y_log10() +
  annotation_logticks(sides = "a") +
  scale_fill_npg() +
  scale_color_npg() +
  theme_bw() +
  labs(x = "Terrain",
       y = "Turnover time (d^-1)",
       title = "Generation times of soil bacteria across terrain") +
  theme(legend.position = "none",
        axis.ticks.y = element_blank())
p_turnover_terrain_7d
```

@@

## Turnover time versus lipid relative abundance

```{r}

gen_calc_data %>% filter(inc_time_d != 0) %>% 
  ggplot(aes(x = rel_area_FID,
             y = u_d,
             color = chain_fctr)) +
  geom_point() +
  scale_color_viridis_d() +
  facet_wrap(~terrain) +
  labs(x = "Relative Area (GC-FID)",
       y = "Turnover (d^-1)",
       color = "Compound class") +
  theme_bw()

## Compound-Specific Enrichment

```{r}
gen_calc_data %>% 
  mutate(compound = fct_reorder(compound, -chain_num)) %>% 
  ggplot(aes(x = at2H,
             y = compound,
             fill = stat(x))) +
  geom_density_ridges_gradient(scale = 3) +
  # Vline showing enrichment strength
  # geom_vline(xintercept = 0.5,
  #            color = "red") +
  facet_wrap(vars(inc_time_d_str), ncol = 1) +
  scale_fill_viridis_c(option = "C") +
  labs(fill = "% D",
       x = "% D",
       y = "Compound") +
  theme_ridges() +
  theme(axis.text.y = element_text(size = 5),
        legend.position = "right",
        legend.key.width = unit(0.2, "line"),
        legend.text = element_text(size = 10))
```

## Compound specific turnover
```{r}
gen_calc_data %>% 
  mutate(compound = fct_reorder(compound, -chain_num)) %>% 
  ggplot(aes(x = u_d,
             y = compound,
             fill = stat(x))) +
  geom_density_ridges_gradient() +
  # Vline showing enrichment strength
  facet_wrap(vars(inc_time_d_str), ncol = 1) +
  scale_fill_viridis_c(option = "C") +
  labs(fill = "µ (d^-1)",
       x = "µ (d^-1)",
       y = "Compound") +
  theme_minimal()
```

## Mean Turnover by Terrain

```{r}
gen_calc_data_summarized %>% 
  group_by(inc_time_d, terrain) %>% 
  summarize(u_d_mn = mean(u_d),
            u_d_max = max(u_d),
            u_d_min = min(u_d),
            gen_d_mn = mean(gen_d),
            gen_d_max = max(gen_d),
            gen_d_min = min(gen_d)) %>% 
  ggplot(aes(x = terrain, 
             y = u_d_mn,
             color = as.character(inc_time_d))) +
  geom_path(color = "black") +
  geom_point() +
  coord_cartesian(ylim = c(0, 0.05)) +
  labs(x = "Terrain",
       y = "Mean Turnover (d^-1)",
       color = "Incubation Time") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

## Mean Turnover Aggregated

```{r}
gen_calc_data_summarized %>% 
  # Calculate means, by terrain
  group_by(inc_time_d, terrain) %>% 
  summarize(u_d_mn = mean(u_d),
            u_d_max = max(u_d),
            u_d_min = min(u_d),
            gen_d_mn = mean(gen_d),
            gen_d_max = max(gen_d),
            gen_d_min = min(gen_d)) %>% 
  # Calculate mean of means
  group_by(inc_time_d) %>% 
  summarize(u_d_mn_ag = mean(u_d_mn),
            u_d_max_ag = max(u_d_mn),
            u_d_min_ag = min(u_d_mn),
            gen_d_mn_ag = mean(gen_d_mn),
            gen_d_max_ag = max(gen_d_mn),
            gen_d_min_ag = min(gen_d_mn)) %>% 
  ggplot(aes(x = 1, 
             y = u_d_mn_ag,
             color = as.character(inc_time_d))) +
  geom_path(color = "black") +
  geom_point() +
  coord_cartesian(ylim = c(0, 0.05)) +
  labs(x = "Terrain",
       y = "Mean Turnover (d^-1)",
       color = "Incubation Time") +
  theme_minimal() +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())

@@

```{r}
# Import lit search data
lit_turnover <- read_xlsx(file.path("data", "literature_turnover_rates.xlsx"))

lit_turnover <- lit_turnover %>% 
  # Arrange by turnover time
  arrange(u_d_mn) %>% 
  # Reassign n values
  mutate(n = seq(from = 1, to = nrow(lit_turnover)))

# Our summarized data
gen_calc_mini <- gen_calc_data_summarized %>% 
  # Calculate mean per terrain per inc time
  group_by(inc_time_d, terrain) %>% 
  summarize(u_d_mn = mean(u_d, na.rm = TRUE),
            u_d_max = max(u_d),
            u_d_min = min(u_d)) %>%
  # Calculate mean of means (combine inc_times)
  group_by(terrain) %>% 
  summarize(u_d_mn = mean(u_d_mn, na.rm = TRUE),
            u_d_max = max(u_d_mn, na.rm = TRUE),
            u_d_min = min(u_d_mn, na.rm = TRUE)) %>% 
  # Rename to match `lit_turnover` tibble
  rename(soil_type = terrain) %>% 
  arrange(u_d_mn) %>% 
  mutate(method = "2H Lipid SIP",
         n = c(17, 18, 19),
    soil_type = case_when(
      soil_type == "Niwot Ridge Tundra" ~ "tundra",
      soil_type == "Gordon Gulch Conifer Forest" ~ "conifer forest",
      soil_type == "Marshall Mesa Grassland" ~ "grassland")
  )

# Add in our data! ^_^
lit_turnover_w_ours <- lit_turnover %>% bind_rows(gen_calc_mini)

lit_turnover_w_ours <- lit_turnover_w_ours %>% 
  mutate(
    source = case_when(
      method == "2H Lipid SIP" ~ "This study",
      TRUE ~ "Literature values"
  ))

# By terrain
